\Huge Don't interpolate your data!

### 2022-11-02 paper/main.tex
add final comments to concepts/assumptions

% text macros
\shorttitle{don't interpolate your data!}
\shortauthors{hogg \& casey}
\newcommand{\sectionname}{Section}

@@

@@

\paragraph{Pixel-convolved line-spread function}
The spectrograph has something like a point-spread function or line-spread function, which, in the case of spectrosccopy, sets the shape of an unresolved spectral line.
In general it depends on the slit or fiber width, the spectrograph resolution and optics, instrument focus, and the properties of the detector.
In what follows we will not build any model of any of this.
Instead we will assume that there is a relatively constant pixel-convolved line-spread function (PCLSF), constant both in time, and constant with respect to the shifts $\Delta x_i$ we see in our data set.
We consider only the PCLSF, because then the sampling by the detector pixels does not require any additional convolution.
That is, when the PCLSF is used to model a spectrum, the projection onto the pixels is just a sampling of the function at the pixel centers, and does not involve any convolution over the face of the pixel.
All that said, we won't explicitly model or use the PCLSF in what follows; we will just assume that our continuous spectral model is a model for the pixel-convolved, finite-resolution spectrum; we won't be doing any convolutions in comparing models and data.

@@

@@

>>>>

% text macros
\shorttitle{don't interpolate your data!}
% Or...
%\shorttitle{Binning is sinning!}
\shortauthors{hogg \& casey}
\newcommand{\sectionname}{Section}

@@

\paragraph{Bit-flag masks}
A bit-flag mask is often used to store meta data about specific pixels in an observation that otherwise cannot be encoded by the spectrum $y_i$ or its asssociated variance tensor $C_i$ (e.g., poorly described line spread function). 
We often want to propagate this meta data to appropriate pixels in the combined spectrum. 
These bit-flag masks are usually encoded as integers with up to $F$ potential flags, allowing for all (or a subset of) flags to be encoded as a single value $\sum^{F}_{f=0} 2^f$. 
This bit-flag mask can be separated into $F$ masks where each has value 1 in the locations where the flag is marked, and 0 in the locations where it is not.

@@

\paragraph{Pixel-convolved line-spread function}
The spectrograph has something like a point-spread function or line-spread function, which, in the case of spectrosccopy, sets the shape of an unresolved spectral line.
In general it depends on the slit or fiber width, the spectrograph resolution and optics, instrument focus, and the properties of the detector.
In what follows we will not build a model of any of this.
Instead we will assume that there is a relatively constant pixel-convolved line-spread function (PCLSF), constant both in time, and constant with respect to the shifts $\Delta x_i$ we see in our data set.
We consider only the PCLSF, because then the sampling by the detector pixels does not require any additional convolution.
That is, when the PCLSF is used to model a spectrum, the projection onto the pixels is just a sampling of the function at the pixel centers, and does not involve any convolution over the face of the pixel.
All that said, we won't explicitly model or use the PCLSF in what follows; we will just assume that our continuous spectral model is a model for the pixel-convolved, finite-resolution spectrum; we won't be doing any convolutions in comparing models and data.

@@

ANDY: discuss with Hogg and check earlier language on spectral representation. Could introduce it earlier as continuous spectral model.

@@

ANDY: Should we mention something about if it is not telluric corrected, and you have many epochs of a source that has perceived radial velocity variations, then you want something like wobble?
